Dispersion Distance and the Matter Distribution of the Universe in Dispersion Space

### 2015-08-05 writeup/referee_response.txt

This was chosen to be roughly the value for star forming galaxies at these
redshifts as measured by the WiggleZ survey. The assumption here is that FRBs
might trace star formation, although this is entirely speculative. It also
provides some contrast with the electrons, since some terms are proportional to
b_e - b_f. This is now stated in the text.

> Also, it would be good to discuss briefly (perhaps
> with a new plot) the dependence of the paper’s conclusions on the
> value of b_f. In principle, variations of b_f could cause interesting
> effects, since b_f affects some of the terms but not others in Eq.
> (22). My guess is that the effects won’t be too big, since Fig. 2
> shows that the integral term is the dominant contribution, but it’d be
> nice to numerically confirm this. If anything, it would be helpful to
> know that the predictions are robust to uncertainties in b_f.

This was a very helpful comment and led us to include a b_f=0.7 line in Figure
3. We conclude that the sensitivity is indeed dominated by the integral term
and that a survey with 10000 events is unlikely to distinguish any signature of
the intrinsic clustering.

Time dependence of b_f should similarly be a small effect on the final
sensitivity, although we agree that the different effects of the bias could be
exploited in a higher precision survey. We've added a paragraph about the
effect of the biases on the various terms in the modelling section.

@@

> 
> ii) To plot Fig. 3, the authors summed over pairs of radial bins.
> However, this hides some of the interesting statistical properties of
> the signal. For example, I would expect the cross power spectrum of
> two widely separated radial bins to be much lower than the cross power
> of two nearby bins. I would like to see some quantification of these
> radial correlations, as it would give readers a better sense for how
> the signal-to-noise scales with bin size, number of bins, etc.

Figure 2 is intended to give a hint of this structure. The integral term and
the cross term are fairly insensitive to radial separation since any
overlapping structure in the radial integral will correlate. The radial
dependence is actually dominated by A(\chi).  As shown in Gigure 2, the local
term drops rapidly at higher separations. We would very much like to show more
curves in the style of Figure 2 but space constrains preclude this.

@@

We've added a brief statement about this in the discussion.  We hope that the
reviewer finds this satisfactory.

> 
> Finally, just an extremely minor pet peeve of mine: can we replace the
> error bars in Fig. 3 with a band around the curve? Real data would
> have scatter, and the error bars wouldn’t be centered on the “truth”.

Our error bars depend on \ell binning and thus a band is inappropriate.
However we agree with the points of the referee and we have thus switched to
filled boxes to approximate a band.  This is consistent with the style in, for
example, Scott Dodelson's text book.

### 2015-08-05 writeup/dm_space_distortions.tex
As re-submitted.

\blue{
The amplitude of the local and cross terms depend on the difference
between the electron bias and highly uncertain FRB bias
and the sign of the cross term depends on
which of these is larger. However, since the
integral term dominates for most radial distance pairs, our final sensitivity
estimates are largely unaffected by this uncertainty (as shown below). In a
high-precision survey the sensitivity of the cross and local terms to the
difference in the biases may help break measurement degeneracies.
}

@@

We consider the sensitivity of a survey with a total of $10000$ dispersion
measures from FRB events distributed uniformly over half the sky.
To give an idea of the overall sensitivity of the survey, we collapse
$C^{ss}_{\ell,ij}$ to a single function of $\ell$ by taking a weighted average
of all pairs of radial bins over the
range $500\,{\rm Mpc}/h$ to $3500\,{\rm Mpc}/h$.
For weights we use the signal over noise-squared
at $\ell=100$, which maximizes the signal to noise at that $\ell$ and
is near optimal at other multipoles.
\blue{
To determine if such a survey would be
able to distinguish between models of FRB clustering we plot the same quantity
for $b_f=0.7$.
}
The result is shown
in Figure~\ref{f:sensitivity}.

@@

We have
shown in Figure~\ref{f:sensitivity}
that a survey detecting $10000$ fast radio bursts of cosmological
origin could detect the
clustering signal\blue{, however such a survey would be mostly sensitive to the
integral term and thus could not distinguish between FRB clustering models}.
This is in rough
approximation to what might be achieved in a reasonable amount of time by the
Canadian Hydrogen Intensity
Mapping Experiment (CHIME)\footnote{\url{http://chime.phas.ubc.ca/}}, the
Square Kilometer Array\footnote{\url{http://www.skatelescope.org/}},
or other upcoming wide-field telescopes.
Looking forward, dispersion-space
clustering could become a precision probe of large-scale structure should
observational factors turn out to be favourable compared to spectroscopic
surveys. The baryon acoustic oscillation feature can be clearly seen in
Figure~\ref{f:terms} in the cross term and both
local-term curves. It may also be possible to extract the BAO feature
from the integral
term using tomography.
This however requires that the statistics of the contribution to dispersion from
the source's environment and host halo to be well understood or small compared to the
contribution from the line-of-sight.

>>>>

\blue{
The amplitude of the local and cross terms depend on the difference
between the electron bias and highly uncertain FRB bias
and the sign of the cross term depends on
which of these is larger. However, since the
integral term dominates for most radial distance pairs, our final sensitivity
estimates are largely unaffected by this uncertainty (as shown below). In a
high-precision survey the sensitivity of the cross and local terms to the
difference in the biases may help break measurement degeneracies, while sign
changes of terms as a function of radial distance are a signature of
bias evolution.
}

@@

We consider the sensitivity of a survey with a total of $10000$ dispersion
measures from FRB events distributed uniformly over half the sky.
To give an idea of the overall sensitivity of the survey, we collapse
$C^{ss}_{\ell,ij}$ to a single function of $\ell$ by taking a weighted average
of all pairs of radial bins over the
range $500\,{\rm Mpc}/h$ to $3500\,{\rm Mpc}/h$.
For weights we use the signal over noise-squared
at $\ell=100$, which maximizes the signal to noise at that $\ell$ and
is near optimal at other multipoles.
\blue{
To determine if such a survey would be
able to distinguish between models of FRB clustering we plot the same quantity
for $b_f=0.8$.
}
The result is shown
in Figure~\ref{f:sensitivity}.

@@

We have
shown in Figure~\ref{f:sensitivity}
that a survey detecting $10000$ fast radio bursts of cosmological
origin could detect the
clustering signal.
This is in rough
approximation to what might be achieved in a reasonable amount of time by the
Canadian Hydrogen Intensity
Mapping Experiment (CHIME)\footnote{\url{http://chime.phas.ubc.ca/}}, the
Square Kilometer Array\footnote{\url{http://www.skatelescope.org/}},
or other upcoming wide-field telescopes.
\blue{Such a survey would be primarily sensitive to the integral 
term and thus rather insensitive to the details of FRB clustering models.}
Looking forward, dispersion-space
clustering could become a precision probe of large-scale structure should
observational factors turn out to be favourable compared to spectroscopic
surveys. The baryon acoustic oscillation feature can be clearly seen in
Figure~\ref{f:terms} in the cross term and both
local-term curves. It may also be possible to extract the BAO feature
from the integral
term using tomography.
This however requires that the statistics of the contribution to dispersion from
the source's environment and host halo to be well understood or small compared to the
contribution from the line-of-sight.
